CP_MSSA

### 2025-03-14 Code/R/Research/CP_MSSA.Rmd
Case of noise mixing

## 5
A <- 20 * exp(ones %o% c(rep(0.05, 7), 0.03, 0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "diff_exp_same_freq"
groups_mssa <- list(1:4)
groups3 <- list(1:2)
groups_cp <- list(1:4)

@@

Ls_mssa <- seq(from = max.r,
               to = N - max.r + 1,
               by = 2)
Ls_cp <- seq(from = max.rcp,
             to = N - max.rcp + 1,
             by = 2)
# Ls_cp <- c(20, 40)
Ls_ho <- seq(from = max.r,
                 to = (N + 1) %/% 2,
                 by = 2)

@@

rmse_L_cpmssa_res <- t(rbind(Ls_cp, rmse_L_cpmssa(R)))
# save(
#   rmse_L_cpmssa_res,
#   file = paste0(
#     "./Research/comp_results/cpmssa_",
#     save_file_name,
#     "_L.RData"
#   )
# )
rmse_L_cpmssa_res[order(rowMeans(rmse_L_cpmssa_res[, -1]), decreasing = FALSE), ] |>
  head() |>
  print()
# 62 1.139832 1.163155 1.211639 1.165164 1.210579 1.182345 1.168282 2.261075 2.241531
# 56 1.102377 1.134577 1.175887 1.130599 1.181898 1.151490 1.109888 2.002356 2.020384
```

>>>>

# 5
# A <- 20 * exp(ones %o% c(rep(0.05, 7), 0.03, 0.03) * 1:N)
# w <- rep(1 / 12, 9)
# phi <- ones %o% rep(0, 9)
# save_file_name <- "diff_exp_same_freq"
# groups_mssa <- list(1:4)
# groups3 <- list(1:2)
# groups_cp <- list(1:4)

## 6
A <- exp(ones %o% c(-rep(0.05, 7), -0.03, -0.03) * 1:N)
w <- rep(1 / 12, 9)
phi <- ones %o% rep(0, 9)
save_file_name <- "noise_mixing"
groups_mssa <- list(1)
groups3 <- list(1)
groups_cp <- list(1)

@@

Ls_mssa <- seq(from = max.r,
               to = N - max.r + 1,
               by = 2)
Ls_cp <- seq(from = max.rcp,
             to = N - max.rcp + 1,
             by = 2)
Ls_ho <- seq(from = max.r,
                 to = (N + 1) %/% 2,
                 by = 2)

@@

rmse_L_cpmssa_res <- t(rbind(Ls_cp, rmse_L_cpmssa(R)))
save(
  rmse_L_cpmssa_res,
  file = paste0(
    "./Research/comp_results/cpmssa_",
    save_file_name,
    "_L.RData"
  )
)
rmse_L_cpmssa_res[order(rowMeans(rmse_L_cpmssa_res[, -1]), decreasing = FALSE), ] |>
  head() |>
  print()
```
